---
title: "Estimating Patient Experience Score"
author: ""
date: ""
output: html_document
---

##Logistic Regression Model with Binary Outcome

The logistic regression model generated below looks at patient experience as an outcome of hospital ownership, hospital type, and overall rating as explained by the [Medicare Hospital General Information dataset](https://data.medicare.gov). Our preliminary model shows hospital overall rating and hospital type as signficant (p<0.05) predictors of patient experience score. 

* Hopsital ownership was defined by five categores: Proprietary, Physician, Voluntary non-profit Church, Voluntary non-Profit Private, Voluntary non-Profit Other, and Government. The reference variable is Government.

** The government category was originally defined as government-state ownership, government-local ownership, government-Hospital District ownership or Authority, and government-federal. We collapsed the 4 dummy variables for government into one government dummy variable (within hospital ownership). 

* The reference variable for the hospital type variable is Acute Care Hospitals. 

* The entire dataset (hospital count = 2151) was used develop this model.

##Final Model

$logit(patient experience) = -7.40 + -0.96X(hospitalownership-Physician) + -1.38X(hospitalownership-Propietry)
+ 0.02X(hospitalownership-Voluntary-non-profit-Church) + -0.02X(hospitalownership-Voluntary-non-profit-Other)
+ -0.16X(hospitalownership-Voluntary-non-profit-Private) + 2.46X(hospitaloverallrating) + 2.13X(hospitaltypeCriticalAccessHospitals)$

```{r, echo = FALSE, message=F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(janitor)
library(stringr)
library(ggridges)
library(ggthemes)
library(forcats)
library(viridis)
library(plotly)
library(knitr)
library(kableExtra)
library(shiny)
library(rvest)
library(httr)
```

```{r, echo = FALSE, message=F}
# Load hospital_data_2.csv below for results of above code chunk
hospital_data_2 <- read_csv("./data/hospital_data_2.csv")
```

```{r, echo = FALSE, message=F}
##logistic modelling - binary outcome (patient experience - above and below national average)

##recode model 
hospital_data_logistic_regression =  hospital_data_2 %>%
filter(patient_experience_national_comparison != "Not Available") %>%
filter(patient_experience_national_comparison != "Same as the national average") %>%
mutate(patient_experience_national_comparison = recode(patient_experience_national_comparison, "Above the national average" = "1", "Below the national average" = "0"))

##making column 9 numeric with lapply
hospital_data_logistic_regression[,9] <- lapply(hospital_data_logistic_regression[,9], as.numeric)

##using glm with binomial distribution for model 
mylogit <- glm(patient_experience_national_comparison ~ hospital_ownership + hospital_overall_rating + hospital_type, data = hospital_data_logistic_regression, family = "binomial"(link = "logit"))



##revising data set to collapse government
hospital_data_logistic_regression_comp <- hospital_data_logistic_regression %>%
mutate(hospital_ownership = recode(hospital_ownership, "Government - Local" = "Government", "Government - State" = "Government", "Government - Hospital District or Authority" = "Government", "Government - Federal" = "Government")) 



##creating function to run regression model
hospitaldata_logm = function(df){
glm(patient_experience_national_comparison ~ hospital_ownership + hospital_overall_rating + hospital_type, data = hospital_data_logistic_regression_comp, family = "binomial"(link = "logit"))
}

hospital_data_lr_df = 
  hospital_data_logistic_regression_comp %>% 
  nest(provider_id:patient_experience_national_comparison) %>%
  mutate(models = map(data, hospitaldata_logm),
         results = map(models, broom::tidy)) %>%
  select(results) %>% 
  unnest() 

hospital_data_lr_df <- hospital_data_lr_df[c(1, 2, 3, 4, 5, 6, 7, 8),]   
```

```{r, echo = FALSE, message=FALSE}
library(kableExtra)
library(pander)
options(knitr.table.format = "html") 

kable(hospital_data_lr_df, caption = "Model Components of our patient experience model") %>%
  kable_styling("striped", full_width = F) %>%
  column_spec(5, bold = T) %>%
  row_spec(7:8, bold = T, color = "white", background = "#D7261E") %>%
  row_spec(3, bold = T, color = "white", background = "#D7261E") 
```



