---
title: "Estimating patient experience score using logistic regression "
author: ""
date: ""
output: html_document
---

#Estimating patient experience score using logistic regression 

*Logistic Model*

The logistic regression model generated below looked at patient experience as an outcome of hospital ownership, hospital type, and overall rating as explained by the Medicare Hospital General Information. We were interested to see how these factors influenced patient experience. Predictors which significantly affected patient experience were overall rating (continuous), hospital type (binary), and Proprietary ownership of the hospital ownership (categorical). We initially used all categories of all variables in our model but with the low overall count of hospitals owned by the government-state, government-local, government-Hospital District or Authority, and government-federal we decided to collapse the dummy variables for government into one governmental categorical variable. The reference variable for the hospital_type variable is acute care hospitals (0). The reference category for the hospital_ownership variable is hospital_ownership_government, and the various dummies include hospital_ownership_Proprietary, hospital_ownership_voluntarynon-profitchurch, hospital_ownership_voluntarynon-profitother, hospital_ownership_voluntarynon-profitprivate. We used the entire dataset to develop this model and also reduced the size of our dataset by creating a binary outcome variable, which may make this model less robust/reproducible.


$logit(patient experience) = -7.40 + -0.96X(hospitalownership-Physician) + -1.38X(hospitalownership-Propietry) + 0.02X(hospitalownership-Voluntary-non-profit-Church) + -0.02X(hospitalownership-Voluntary-non-profit-Other) + -0.16X(hospitalownership-Voluntary-non-profit-Private) + 2.46X(hospital_overall_rating) + 2.13X(hospital_type_CriticalAccessHospitals)$


```{r, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(janitor)
library(stringr)
library(ggridges)
library(ggthemes)
library(forcats)
library(viridis)
library(plotly)
library(knitr)
library(kableExtra)
library(shiny)
library(rvest)
library(httr)
```

```{r, echo = FALSE, message=F}
# Load hospital_data_2.csv below for results of above code chunk
hospital_data_2 <- read_csv("./data/hospital_data_2.csv")
```

```{r, echo = FALSE, message=F}
##logistic modelling - binary outcome (patient experience - above and below national average)

##recode model 
hospital_data_logistic_regression =  hospital_data_2 %>%
filter(patient_experience_national_comparison != "Not Available") %>%
filter(patient_experience_national_comparison != "Same as the national average") %>%
mutate(patient_experience_national_comparison = recode(patient_experience_national_comparison, "Above the national average" = "1", "Below the national average" = "0"))

##making column 9 numeric with lapply
hospital_data_logistic_regression[,9] <- lapply(hospital_data_logistic_regression[,9], as.numeric)

##using glm with binomial distribution for model 
mylogit <- glm(patient_experience_national_comparison ~ hospital_ownership + hospital_overall_rating + hospital_type, data = hospital_data_logistic_regression, family = "binomial"(link = "logit"))



##revising data set to collapse government
hospital_data_logistic_regression_comp <- hospital_data_logistic_regression %>%
mutate(hospital_ownership = recode(hospital_ownership, "Government - Local" = "Government", "Government - State" = "Government", "Government - Hospital District or Authority" = "Government", "Government - Federal" = "Government")) 



##creating function to run regression model
hospitaldata_logm = function(df){
glm(patient_experience_national_comparison ~ hospital_ownership + hospital_overall_rating + hospital_type, data = hospital_data_logistic_regression_comp, family = "binomial"(link = "logit"))
}

hospital_data_lr_df = 
  hospital_data_logistic_regression_comp %>% 
  nest(provider_id:patient_experience_national_comparison) %>%
  mutate(models = map(data, hospitaldata_logm),
         results = map(models, broom::tidy)) %>%
  select(results) %>% 
  unnest() 

hospital_data_lr_df <- hospital_data_lr_df[c(1, 2, 3, 4, 5, 6, 7, 8),]   
```

```{r}
library(kableExtra)
library(pander)
options(knitr.table.format = "html") 

kable(hospital_data_lr_df, caption = "Model Components of our patient experience model") %>%

kable_styling(bootstrap_options = c("striped", "hover"))

##May not be able to run with package kableExtra

kable(hospital_data_lr_df, caption = "Model Components of our patient experience model") %>%

  kable_styling("striped", full_width = F) %>%
  column_spec(5, bold = T) %>%
  row_spec(7:8, bold = T, color = "white", background = "#D7261E") %>%
  row_spec(3, bold = T, color = "white", background = "#D7261E") 
```



